Photosynthesis Course Note

### 2016-07-11 Complex Geometry - index of notations by taper.tex
Addint license notes too all documents.

\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

@@

	\subsection{Lecture 6 Sheaf \& Cohomology (20160315)}
	pp. A:
		\begin{itemize}
			\item Stalk $\mathcal{F}_x$.
			\item germ
			\item Directed partial order set
			\item Directed System
		\end{itemize}
	pp. B:
		\begin{itemize}
			\item Directed limit
		\end{itemize}
	pp. C:
	\begin{itemize}
		\item Exact Complex/ Exact Sequence.
		\item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
		\item
	\end{itemize}
	pp. D:
	\begin{itemize}
		\item Čech cohomology
	\end{itemize}
	pp. E:
	\begin{itemize}
		\item q-cochain
		\item coboundary operator. $\delta$.
		\item $Z^p(U,\mathcal{F})$ = Ker.
		\item $B^p(U,\mathcal{F})$ = Im.
		\item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
	\end{itemize}
		\subsubsection{Notes of Čech Cohomology with Coeficients in a Sheaf}
		pp.1:
		\begin{itemize}
			\item q-simplex $\sigma$.
			\item support $|\sigma|$.
			\item q-cocain
			\item $C^q(U,\mathcal{F})$
			\item Coboundary Operator $\delta$.
		\end{itemize}
		pp.2,3,4:
		\begin{itemize}
			\item Cochain Complex
			\item Čech cohomology
			\item cocycle
			\item cochain
			\item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
			\item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
		\end{itemize}

@@

\end{thebibliography}
\end{document}

>>>>

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

@@

	\subsection{Lecture 6 Sheaf \& Cohomology (20160315)}
	pp. A:
		\begin{itemize}
			\item Stalk $\mathcal{F}_x$.
			\item germ
			\item Directed partial order set
			\item Directed System
		\end{itemize}
	pp. B:
		\begin{itemize}
			\item Directed limit
		\end{itemize}
	pp. C:
	\begin{itemize}
		\item Exact Complex/ Exact Sequence.
		\item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
		\item
	\end{itemize}
	pp. D:
	\begin{itemize}
		\item Čech cohomology
	\end{itemize}
	pp. E:
	\begin{itemize}
		\item q-cochain
		\item coboundary operator. $\delta$.
		\item $Z^p(U,\mathcal{F})$ = Ker.
		\item $B^p(U,\mathcal{F})$ = Im.
		\item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
	\end{itemize}
    \subsubsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
		pp.1:
		\begin{itemize}
			\item q-simplex $\sigma$.
			\item support $|\sigma|$.
			\item q-cocain
			\item $C^q(U,\mathcal{F})$
			\item Coboundary Operator $\delta$.
		\end{itemize}
		pp.2,3,4:
		\begin{itemize}
			\item Cochain Complex
			\item Čech cohomology
			\item cocycle
			\item cochain
			\item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
			\item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
		\end{itemize}

@@

\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-07-11 Photosynthesis Course Note.tex
Addint license notes too all documents.

>>>>

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
